---
title: "Business Analytics – MIS17: Assignment 1"
output: html_notebook
---
```{r}
require(xlsx)
library(tidyverse)
df <- read.xlsx("MIS171-2020-T2-A1.xlsx", "Data")
head(df)
```

# Univariate analysis
### 1.1 Profile of event types
##### Frequency count
```{r}
table(df$EventType)
```
##### Histogram of event types
```{r}
ggplot(df, aes(x=EventType)) + geom_histogram(stat="count")
```

### 1.2 Summary of number of guests
##### Summary statistics of guests
```{r}
summary(df$Guests)
```

##### Histogram of guest count
```{r}
ggplot(df, aes(x=Guests)) + geom_histogram(bins=10)
```
### 1.3 Number of guests outliers
##### Boxplot to reveal outliers
```{r}
ggplot(df, aes(x=Guests)) + geom_boxplot()

```
The boxplot reveals 1 outlier: the event with 327 guests 

### 1.4 Profile of event size 
##### Transforming number of guests to specified categories
```{r}
df$EventSize <- cut(df$Guests,
                    breaks = c(-Inf, 10, 25, 50, 100, Inf),
                    labels = c("Micro", "Mini", "Small", "Medium", "Large")
                    )
```

##### Summary statistics of event size
```{r}
summary(df$EventSize)
```
##### Histogram of event size
```{r}
```


```{r}
ggplot(df, aes(x=EventSize)) + geom_histogram(stat="count", bins=10)
```

### 1.5 Profile of venues
##### Frequency table of venue
```{r}
table(df$Venue)
```
##### Histogram of venues
```{r}
ggplot(df, aes(x=Venue)) + geom_histogram(stat="count")
```

### 1.5 Summary of profit
### profit summary statistics
```{r}
summary(df$Profit)
```
### Histogram of profits
```{r}
ggplot(df, aes(x=Profit)) + geom_histogram( bins=10)
```

### 1.6 Profit outliers
##### Boxplot of profits
```{r}
ggplot(df, aes(x=Profit)) + geom_boxplot()
```


### 1.8 Summary of satisfaction
### Satisfaction summary statistics
```{r}
summary(df$Satisfaction)
```
### Histogram of satisfaction
```{r}
ggplot(df, aes(x=Satisfaction)) + geom_histogram( bins=10)
```

### 1.9 Satisfaction outliers
##### Boxplot of satisfaction
```{r}
ggplot(df, aes(x=Satisfaction)) + geom_boxplot()
```

# Bivariate analysis
### 2.1 Differences in the average Profit between different Event Types


```{r}
tapply(df$Profit, df$EventType, summary)

ggplot(df, aes(x=EventType, y=Profit)) + 
    geom_boxplot()

```

### 2.2 Correltaion between profits and satisfaction

```{r}
library("Hmisc")
res <- rcorr(df$Profit, df$Satisfaction)
res

ggplot(df, aes(x=Satisfaction, y=Profit)) + 
  geom_point()+
  geom_smooth(method=lm, , se=FALSE)
```
### Relationship between event size and profit

```{r}
ggplot(df, aes(x=EventSize, y=Profit)) + 
    geom_boxplot()
```
```{r}

tapply(df$Profit, df$EventSize, summary)
```
### Relationship between satisfaction and venue
```{r}
tapply(df$Satisfaction, df$Venue, summary)
```
```{r}
ggplot(df, aes(x=Venue, y=Satisfaction)) + 
    geom_boxplot()
```




